%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{charter}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{charter}
\usepackage{microtype}
% \usepackage{ragged2e}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{-4pt}\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
    \item\small{
        \textbf{#1}{: #2 \vspace{-3pt}}
    }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
    \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}l}
    \textbf{\Large Grant Lemons}        & Email: \href{mailto:grant0lemons@gmail.com}{grantlemons@aol.com}           \\
                                        & Mobile: \href{tel:+2149806898}{(+1) 214-980-6898}                             \\
                                        & LinkedIn: \href{https://www.linkedin.com/in/grant-lemons/}{grant-lemons}      \\
\end{tabular*}
\vspace*{-.8cm}


%-----------EDUCATION-----------------
\section{Education}
    \resumeSubHeadingListStart
    \resumeSubheading
        {Colorado School of Mines}{Golden, CO}
        {Aug. 2023 -- Present}{}
    \vspace{-.2cm}
    \resumeSubheading
        {Alcuin School}{Dallas, TX}
        {Aug. 2019 -- May 2023}{}
    \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
    \resumeSubHeadingListStart
    \resumeSubheading
        {Headstorm}{Dallas, TX}
        {Software Consulting Intern}{Summer 2023}\\
        \vspace{0.3cm}

        \textbf{Constellation Staffing App v2}\\
        I worked on an internal project focused on refreshing the visuals and backend of the internal Constellation Staffing Application as a part of the Headstorm Internship Program.
        The project involved building a new frontend from the ground up as we migrated to a GraphQL backend as well as implementing better coding standards and integration testing.
        As a part of the Internship Program, I learned valuable Project Management skills through occasionally running scrum ceremonies.
        Through this project I learned React, GraphQL, and some Project Management skills.
        \vspace{0.1cm}
    \resumeSubheading
        {Capstone Project}{Dallas, TX}
        {Alcuin School}{Aug. 2023 -- Feb. 2023}\\
        \vspace{0.3cm}

        \textbf{Advisory Generator}\\
        I successfully created and delivered a multi-tier application to create and manage faculty---student mentorship groups composed of students and teachers as my capstone project.
        The project was based on the needs of the Dean of Students, whom I interviewed for project requirements and acted as my client in this project.\\
        \vspace{0.1cm}
        The project relied on AWS for Authentication and Authorization using Cognito, static web hosting of the frontend on S3, as well as the hosting of a graph database and the backend on ECS using Fargate.
        Through the frontend of my app I learned the Svelte web framework and was exposed to CSS, and through the backend I matured my understanding of the Rust programming language.\\
        \vspace{0.1cm}
    \resumeSubheading
        {Headstorm}{Dallas, TX}
        {Software Consulting Intern}{Summer 2022}\\
        \vspace{0.3cm}

        \textbf{Constellation Staffing App}\\
        I worked on an internal application structured to mimic a client project as a part of the Headstorm Internship Program. This project involved building a staffing metrics and scheduling application from the ground up to serve the needs of the company's directors. The application boasted a robust feature set that allowed company leadership to assign resources to projects and view person and project specific allocation.\\
        \vspace{0.1cm}
        I developed a majority of the backend and database work on this project. My ETL program performed automatic database updates using AWS Lambda. Through this I learned TypeScript, Express.js, Sequelize ORM, and PostgreSQL.\\
        \vspace{0.1cm}
        I worked with a team of interns and consultants in an agile scrum environment. I presented the project outcomes to the company as a whole upon the completion of the internship.\\
    \resumeSubHeadingListEnd


%-----------CERTIFICATIONS------------
\section{Certifications}
    \resumeSubHeadingListStart
        \item{
            \textbf{AWS Solutions Architect --- Associate}\\
            \hspace{.3cm}\small Issued: Aug. 2022\\
            \hspace{.3cm}\small Expires: Aug. 2025\\
            \hspace{.3cm}\small Credential ID: S8XVNC12QBF41B57\\
        }
    \resumeSubHeadingListEnd


% --------PROGRAMMING SKILLS------------
\section{Programming Skills}
    \resumeSubHeadingListStart
        \item{
            \textbf{Languages}{: Rust, Java, Python, TypeScript, SQL, Bash/Zsh}
        }
        \vspace{-.3cm}
        \item{
            \textbf{Technologies}{: AWS, Docker, React, Git, Playwright, PostgreSQL, Neo4J}
        }
    \resumeSubHeadingListEnd
\end{document}
